### 2019-09-14 2019_neurips_vigil/model.tex
summary output unit

This unit also output the temporal class weights that will be used in the Reasoning Unit. It gives access to a temporal information for the current words. (last, latest, now, none temporal)

@@

\subsection{Summary Object  Unit}

The goal of the Summary Object

>>>>

This unit also outputs the temporal class weights that will be used in the Reasoning Unit. It gives access to a temporal information for the current words (last, latest, now, none temporal).

@@

\subsection{Summary  Unit}

The  Summary Unit is the last unit of the SAMCell. It is responsible to output the new summary object. It first picks which object is relevant between the object extracted from memory and the visual object extracted from the image. Once the relevant object is picked, it is combined with the former summary object through a linear layer to become the new summary object. It is the final step of the SAMCell reasoning cycle.
